---
title: "Data Product Development - Linear Regression and Prediction"
author: "Siying R"
date: "June 7, 2020"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```
## Introduction

The application allows the users to select 2 to 3 variables (name as **Y**, **X** and **Z** below) and fit them to the Fitting Linear Models and make prediction with the values the user put in. 

The web application can be accessed here: *<https://sruan.shinyapps.io/C9W4/>*. There are 6 plots on the mail panel. It may take a while for to load.

The data used is the **state.x77** in the **R Datasets Package** named *datasets*. 

## Use the WebApp

Prefer to select LifeExp as the Y variable, as the last plot was base on LifeExp being the Y variale. 

Users can:

  1. Change the line size in the first plot. 
  2. Select *X* or/and *Z* variable to see the linear model. 
  3. Input a value for the selecte variable *X* or/and *Z* and make a prediction.
  4. Select another varible other than the *X* variable to display on the scatter plot. 
  5. Change the color of the circle of the dots on the selected varible on the last plot. 
  

## Data Exploration
The points of each varialble overlap each other and are hard to see.

```{r, loopnoformat, fig.align='center', warning=FALSE, message=FALSE}
library(datasets)
library(plotly)
statedata <- as.data.frame(state.x77)
statedata <- statedata[order(statedata$`Life Exp`),]

  fig <- plot_ly(statedata, type = 'scatter', mode = 'markers')
for (i in 1:8){
  fig<- add_trace(fig, x = ~`Life Exp`, y=statedata[[i]], 
                  name = names(statedata[i]), type = 'scatter')
              }
  fig
```

## Data Formating

- Turn Illiteracy, Murder and HS Grad into number of people.
- Turn the Area into Population Density. 
- Refer the min-max-mean data in the table below to input *X* and *Z* value. 
```{r, formatdata, echo=FALSE, comment="", warning=FALSE, message=FALSE, fig.align='left'}
library(datasets)
library(dplyr)
statedata <- as.data.frame(state.x77)
statedata$Illiteracy <- ceiling(statedata$Population*
                                  statedata$Illiteracy/100)
statedata$Murder <- ceiling(statedata$Population/1000*
                              statedata$Murder)
statedata$`HS Grad` <- ceiling(statedata$Population*
                                 statedata$`HS Grad`/100)
statedata$Area <- statedata$Area/statedata$Population
mind <- summarise_all(statedata,min)
maxd <- summarise_all(statedata,max)
meand <- summarise_all(statedata,mean)
statedata <- rbind(mind,maxd,meand)
rownames(statedata) <- c("Min", "Max", "Mean")
statedata$Area <- round(statedata$Area,2)
statedata

```

## Plotly After Formating
The points of each varialble have less overlap and easier to see. We can better see the relationship between each variable and the life expectancy. 

```{r, loopformated, fig.align='center', warning=FALSE, message=FALSE}
library(datasets)
library(plotly)
statedata <- as.data.frame(state.x77)
statedata$Illiteracy <- ceiling(statedata$Population*statedata$Illiteracy/100)
statedata$Murder <- ceiling(statedata$Population/1000*statedata$Murder)
statedata$`HS Grad` <- ceiling(statedata$Population*statedata$`HS Grad`/100)
statedata$Area <- statedata$Area/statedata$Population
statedata <- statedata[order(statedata$`Life Exp`),]

  fig <- plot_ly(statedata, type = 'scatter', mode = 'markers')
for (i in 1:8){
  fig<- add_trace(fig, x = ~`Life Exp`, y=statedata[[i]], name = names(statedata[i]), type = 'scatter')
}
  fig
```



